Wall and LR Fish

### 2024-03-01 Fish Data Analysis/Walls and LR Turns.qmd
Re graphing with new data

eight_fish_turning_data <- read.csv("Data/eight_fish_data_turning.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
                           dplyr::select(-c("Singles")) %>%
                           mutate(Type = "Eight Fish")

single_fish_turning_data <- read.csv("Data/single_fish_data_turning.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
                           dplyr::select(-c("Singles")) %>%
                           mutate(Type = "Combined Single")
```

@@

eight_fish_turning_base <- glm(turn_bool ~ 1,
                               family = "binomial",
                               data = eight_fish_turning_data %>% filter(Flow == "Still Water"))

eight_fish_turning_step <- stepAIC(eight_fish_turning_base, 
                                   list(upper = ~ Wall_Dist*Fish_Num_Ratio*Ablation*Darkness, lower = ~1), 
                                   direction = "both",
                                   trace = F)
Anova(eight_fish_turning_step)

@@

single_fish_turning_step <- stepAIC(single_fish_turning_base, 
                                   list(upper = ~ Wall_Dist*Fish_Num_Ratio, lower = ~1), 
                                   direction = "both",
                                   trace = F)
Anova(single_fish_turning_step)

>>>>

eight_fish_turning_data <- read.csv("Data/eight_fish_data_turning.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
                           dplyr::select(-c("Singles")) %>%
                           mutate(Type = "Eight Fish") %>%
                           mutate(Min_Wall = pmin(Right_Wall_Dist,Left_Wall_Dist))

single_fish_turning_data <- read.csv("Data/single_fish_data_turning.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
                           dplyr::select(-c("Singles")) %>%
                           mutate(Type = "Combined Single")

eight_fish_data_sum  <- eight_fish_turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               se_right_turn = sd_right_turn/sqrt(n()),
                                               n = n()) %>%
                                     ungroup()

eight_fish_data_sum_away  <- eight_fish_turning_data %>% na.omit %>% filter(Min_Wall >= 2) %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               se_right_turn = sd_right_turn/sqrt(n()),
                                               n = n()) %>%
                                     ungroup()
```

```{r}
eight_fish_still <- ggplot(eight_fish_data_sum_away %>% filter(Flow == "Still Water"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.25) +
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

eight_fish_flow <- ggplot(eight_fish_data_sum %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.25) +
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

eight_fish_still
eight_fish_flow

@@

eight_fish_turning_base <- glm(turn_bool ~ 1,
                               family = "binomial",
                               data = eight_fish_turning_data %>% filter(Flow == "Still Water" & Min_Wall > 2))

eight_fish_turning_step <- stepAIC(eight_fish_turning_base, 
                                   list(upper = ~ Left_Wall_Dist*Right_Wall_Dist*Fish_Num_Ratio*Ablation*Darkness, lower = ~1), 
                                   direction = "both",
                                   trace = F)
Anova(eight_fish_turning_step)

@@

single_fish_turning_step <- stepAIC(single_fish_turning_base, 
                                   list(upper = ~ Left_Wall_Dist*Right_Wall_Dist*Fish_Num_Ratio, lower = ~1), 
                                   direction = "both",
                                   trace = F)
Anova(single_fish_turning_step)
